---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(palmerpenguins)
library(tidyverse)

data("penguins")
```


## Introduction to lab

We are going to work with the data set *penguins_raw* from the
`palmerpinguins` package. 

Data set description: 
*A tibble with 344 rows and 17 variables*


| Variable Name     | Description                                                                             |
| ----------------- | --------------------------------------------------------------------------------------- |
| studyName         | Sampling expedition from which data were collected, generated, etc.                     |
| Sample Number     | an integer denoting the continuous numbering sequence for each sample                   |
| Species           | a character string denoting the penguin species                                         |
| Region            | a character string denoting the region of Palmer LTER sampling grid                     |
| Island            | a character string denoting the island near Palmer Station where samples were collected |
| Stage             | a character string denoting reproductive stage at sampling                              |
| Individual ID     | a character string denoting the unique ID for each individual in dataset                |
| Clutch Completion | a character string denoting if the study nest observed with a full clutch, i.e., 2 eggs |
| Date Egg          | a date denoting the date study nest observed with 1 egg (sampled)                       |
| Culmen Length     | a number denoting the length of the dorsal ridge of a bird's bill (millimeters)         |
| Culmen Depth      | a number denoting the depth of the dorsal ridge of a bird's bill (millimeters)          |
| Flipper Length    | an integer denoting the length penguin flipper (millimeters)                            |
| Body Mass         | an integer denoting the penguin body mass (grams)                                       |
| Sex               | a character string denoting the sex of an animal                                        |
| Delta 15 N        | a number denoting the measure of the ratio of stable isotopes 15N:14N                   |
| Delta 13 C        | a number denoting the measure of the ratio of stable isotopes 13C:12C                   |
| Comments          | a character string with text providing additional relevant information for data         |



## Stringr

### Excercise 1

Create a vector that contains at least three different characters
```{r create-vector, exercise=TRUE}

```


```{r create-vector-hint}
my_string <- c()
```

```{r create-vector-solution}
my_string <- c("my string", "has", "3 things!")
```


### Excercise 2

What function would you use to answer the following question:

*How many characters has the longest comment on the penguins_raw data set?*. 
(Remember the data set is called `penguins_raw` and the variable is called
`Comments`)

```{r number-characters, exercise=TRUE}

```
```{r number-characters-hint}
str_length()
```

```{r number-characters-solution}
str_length(penguins_raw$Comments)
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-solution}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

